Crop diversification in a game against nature in a mediterranean agro-ecosystem

### 2020-01-24 risk-percption.Rmd
birth-death processes

```{r}
agents <- tibble(id = 1:100, 
                 alpha = 1.5,
                 beta = 1.5,
                 risk = alpha / (alpha + beta))
```

@@

@@

moran_birth_death <- function(agents, r = 1) {
```{r}
load('../Silvanus/R/sysdata.rda')
life_table
fertility_shape <- 4.579627
fertility_scale <- 0.1

die <- function(individuals, food_ratio = 0.7) {
  individuals %>%
        left_join(life_table, by = 'age') %>%

```{r}
reduce(1:600, ~reproduce(.x) %>% die , .init = agents2 %>% mutate(age = sample.int(80, size = 150, replace = TRUE))) %>%
```

>>>>

```{r}
agents <- tibble(id = 1:150, 
                 alpha = 1.5,
                 beta = 1.5,
                 risk = alpha / (alpha + beta))
```

@@

```{r}
agents2 <- agents %>%
  select(id) %>%
  mutate(age = 1)

moran_birth_death <- function(agents, r = 1) {
  n <- nrow(agents)
  birth_index <- sample.int(n, size = r)
  death_index <- sample.int(n, size = r)
  newborn <- agents %>%
    filter(row_number() %in% birth_index) %>%
    mutate(age = 1)

  agents %>%
    filter(!row_number() %in% death_index) %>%
    mutate(age  = age + 1) %>%
    bind_rows(newborn)
}

reduce(1:1000, ~moran_birth_death(., r = 4), .init = agents2) %>%
  pull(age) %>%hist
```

```{r}
load('../Silvanus/R/sysdata.rda')
life_table
fertility_shape <- 4.579627
fertility_scale <- 0.1
survivor_scale <- 0.1
```

```{r}
reproduce <- function(individuals, food_ratio = 0.7) {
  individuals %>%
    left_join(life_table, by = 'age') %>% 
    mutate(fertility_reduction = pgamma(food_ratio, shape = fertility_shape, scale = fertility_scale),
           reproduced = rbernoulli(n(), fertility_rate / 2 * fertility_reduction)) %>% # divide by two to make everyone female
    filter(reproduced == TRUE) %>% # if nrows == 0, will give a (for some reason unsuppressible) warning
    tally %>% # count births per household
    uncount(n) %>% # repeat rows based on birth count per household
    mutate(age = 0) %>%
    bind_rows(individuals, .) %>%
    ungroup # check for filled na's here?
}

die <- function(individuals, food_ratio = 0.7) {
  individuals %>%
        left_join(life_table, by = 'age') %>% 
    mutate(survival_reduction = pgamma(pmin(1, food_ratio), shape = survival_shape, scale = survivor_scale),
           survived = rbernoulli(n(), survival_rate * survival_reduction)) %>%
    filter(survived == TRUE) %>%
    select(-c(fertility_rate:survived)) %>%
    mutate(age = age + 1)
}

```{r}
reduce(1:600, ~reproduce(.x) %>% die , .init = agents2 %>% mutate(age = sample.int(80, size = 150, replace = TRUE))) %>%
  pull(age) %>% hist
```

@@

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
